\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]

\textbf{Ganesh P Nischay} \\
\indent ##7899, 10th cross\\
\indent Subhash Nagar, Nelamangala\\
\indent Bangalore Rural, Karnataka - 562123\\
\indent Email-id : \textbf{ganeshnischayp@gmail.com} \\
\indent Mobile No.: \textbf{8050435989} \\
\indent Github: \textbf{https://github.com/ganeshnischayp} \\



\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l @{\hskip 0.15in} l }
\hline
\textbf{Examination} & \textbf{University}  & \textbf{Year} & \textbf{CPI/\%} \\
\hline
Under Graduate Specialization:\,\, & \textit{Information Technology} \\
Under Graduation & NITK Surathkal & 2016-2020 & 7.35/10 \\
\\
Pre-University Specialization: & \textit{PCMB} \\
Pre-University Education & Vidya Mandir Ind. Pre-University college, Bangalore  & 2016 & 96\\
Secondary Education(KSEEB) & Bhoruka English School, Bangalore  & 2014 & 96.32\\
\hline
\end{tabular}
%\end{center}
%\end{table}
\\ \\






\resheading{\textbf{PROJECTS} }\\[\lsep]
\begin{itemize}

\item \textbf{Searching a element in O(1)
}  \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Used Bloom filters
	    \begin{itemize}\itemsep \isep
	    \item It is a space-efficient probabilistic data structure that is used to test whether an element is a member of a set or not.
	    \item It is used by Facebook and Gmail to check username is taken or not.
	    \end{itemize}
	\end{itemize}
	

\item \textbf{Players draft system using Stable Matching
}  \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Used Gale Shapley's algorithm to sort players to their teams.
	
	\end{itemize}
	\item \textbf{Sports Vending System
}  \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Developed to website framework to create a online platform for lending sports equipments
	
	\end{itemize}

\item \textbf{Multi-User chat application 
}  \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Used socket programming to share messages and files through computers in the same network.
	
	\end{itemize}
	
	

	
	\item \textbf{Arkanoid Game
}  \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Used Shell Script to code arkanoid game.
	
	\end{itemize}
	
	
	
	
	

	
\end{itemize}



\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Languages : C,C++,python, Java, HTML}.
\item \noindent \textbf{Embedded Processors : Arduino, Raspberry Pi}.
\item \noindent \textbf{Has an idea of: Git, JavaScript, Node.js, }.
\end{itemize}

\resheading{\textbf{RELEVANT COURSE WORK} }\\[\lsep]
\begin{itemize}
\item \noindent Data Structures and Algorithms, Digital Design and Computer Organization, Design and Analysis of Algorithms, UNIX Programming, Operating Systems, Networks, Computer Graphics, Object Oriented Programming, Microprocessors
\end{itemize}

\resheading{\textbf{POSITION OF RESPONSIBILITY} }\\[\lsep]
\begin{itemize}
\item \noindent Executive Member of IET NITK.
\item \noindent Internship Coordinator in NITK.
\item \noindent Executive Member of Corporate Hospitality and Publicity committees( INCIDENT 18 NITK).
\newline
\newline
\end{itemize}

\resheading{\textbf{ACHIEVEMENTS} }\\[\lsep]
\begin{itemize}
\item \noindent Best Student of the Year in 10th(2014)
\item \noindent Secured 6751 rank in JEE Mains(May 2016)
\item \noindent Secured 959 rank in CET(May 2016)
\end{itemize}


\resheading{\textbf{INTEREST AND HOBBIES} }\\[\lsep]
\begin{itemize}
\item \noindent Written and Directed a play in PARVA 2017
\item \noindent Emerging Technology, Reading books, Movies, Sports.


\end{itemize}

\end{document}

